Achieving maximum possible precision on stellar radial-velocity measurements in multi-epoch spectroscopy

### 2017-12-17 paper/paper.tex
more of the same

Fundamentally, what we have shown is that a data-driven model for
stellar spectra can be accurate enough to deliver
radial-velocity (\RV) measurements that saturate information-theoretic
bounds.
It is not surprising that an accurate model of a stellar spectrum
yields good cross-correlation \RV\ measurements.
What is interesting (at least to us) is that there is sufficient
spectral information in a typical exoplanet-related \RV\ observing
program to determine the mean stellar spectrum to sufficient
quality that the \RV\ measurements are close to the best that can
theoretically be made.
It means that the information in the data that goes into determining
the mean stellar spectrum does not come at the expense (in any sense)
of the \RV\ information.

>>>>

This \documentname\ reports good news for exoplanet-related
radial-velocity (\RV) experiments.
First and foremost, we have shown that a data-driven model for
stellar spectra can be accurate enough to deliver
\RV\ measurements that saturate information-theoretic
bounds.
It is not surprising that an accurate model of a stellar spectrum
yields good cross-correlation \RV\ measurements.
What is interesting (at least to us) is that there is sufficient
spectral information in a typical observing
program to determine the mean stellar spectrum to sufficient
quality that the \RV\ measurements are close to the best that can
theoretically be made.
It means that the information in the data that goes into determining
the mean stellar spectrum does not come at the expense (in any sense)
of the \RV\ information.
It also means that \RV\ experiments do not rely on having good models
of stellar spectra; no physical model of a star or its photosphere
is required.
